---
title: "Homework 8"
author: "Kevin Jin"
date: "4/24/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1
**Step 1**: Specify a model.

Proportion of medically insured adults: $X \sim Bern(\omega)$ 

**Step 2**: Identify null ($H_0$) and alternative ($H_\alpha$) hypotheses.

$H_0: \omega = \omega_0 = 0.281$

$H_\alpha: \omega \neq 0.281$

**Step 3**: Specify a test statistic.

$z = \frac{\bar{X}-\omega_0}{\sqrt{\frac{\omega_0(1-\omega_0)}{n}}} \sim N(0,1)$

**Step 4**: Compute the observed value of the test statistic.

$\bar{X} = \frac{30}{75} = 0.4$

$z = \frac{0.4-0.281}{\sqrt{\frac{0.281(1-0.281)}{75}}} = 0.292767347$

**Step 5**: Compute the p-value under $H_0$, where $p=P$.

```{r}
x_bar <- 30 / 75
w_0 <- 0.281
n <- 75
z <- (x_bar - w_0) / sqrt(w_0 * (1 - w_0) / n) 
  
2 * (1 - pnorm(abs(z), mean = 0, sd = 1))
```

**Step 6**: Specify a significance level $\alpha$.

We select the p-value range of $(0.01, 0.05]$, making it statistically 
significant and placing it within significance level $\alpha = 0.05$.

**Step 7**: Compare the p-value and the significance level $\alpha$.

The p-value $= 0.0218614 < \alpha = 0.05$, indicating that we can reject $H_0$; 
therefore, there is a statistically significant difference between the 
proportion of college graduates age 21-24 not medically insured and the
nationwide proportion of adults not medically insured.

```{r}
prop.test(30, 75, p = 0.281, alternative = "two.sided")
```

## Problem 2
**Step 1**: Specify a model.

Proportion of iPhone returns: $X \sim Bern(\omega_x)$ 

Proportion of Galaxy returns: $Y \sim Bern(\omega_y)$ 

**Step 2**: Identify null ($H_0$) and alternative ($H_\alpha$) hypotheses.

$H_0: \omega_x - \omega_y = 0$

$H_\alpha: \omega_x - \omega_y < 0$

**Step 3**: Specify a test statistic.

$z = \frac{\bar{X}-\bar{Y}}{\sqrt{\hat{\omega}(1-\hat{\omega})(\frac{1}{n_x}+\frac{1}{n_y})}} \sim N(0,1)$

$\hat{\omega} = \frac{n_x\bar{x}+n_y\bar{y}}{n_x+n_y}$

**Step 4**: Compute the observed value of the test statistic.

$\bar{X} = \frac{14}{150} = 0.09\bar{3}$

$\bar{Y} = \frac{15}{125} = 0.12$

$\hat{\omega} = \frac{150 * 0.09\bar{3}+125*0.12}{150+125} = 0.105\bar{45}$

$z = \frac{0.09\bar{3}-0.12}{\sqrt{0.105\bar{45}(1-0.105\bar{45})(\frac{1}{150}+\frac{1}{125})}} = -0.716916$

**Step 5**: Compute the p-value under $H_0$, where $p=P$.

```{r}
n_x <- 150
n_y <- 125
x_bar <- 14/n_x
y_bar <- 15/n_y
w_hat <- (n_x * x_bar + n_y * y_bar) / (n_x + n_y)
z <- (x_bar - y_bar) / sqrt(w_hat * (1 - w_hat) * (1 / n_x + 1 / n_y)) 
  
pnorm(z, mean = 0, sd = 1)
```

**Step 6**: Specify a significance level $\alpha$.

We select the p-value range of $(0.01, 0.05]$, making it statistically 
significant and placing it within significance level $\alpha = 0.05$.

**Step 7**: Compare the p-value and the significance level $\alpha$.

The p-value $= 0.2367125 > \alpha = 0.05$, indicating that we cannot reject 
$H_0$; therefore, we cannot conclude that there is statistical evidence that 
iPhones have a smaller chance of being returned than Galaxys.

```{r}
prop.test(c(14, 15), c(150, 125), alternative = "less")
```

## Problem 3
**Step 1**: Specify a model.

Fathers' ages: $X \sim N(\mu_x,\sigma^2_x)$ 

Mothers' ages: $Y \sim N(\mu_y,\sigma^2_y)$ 

**Step 2**: Identify null ($H_0$) and alternative ($H_\alpha$) hypotheses.

$H_0: \mu_x - \mu_y = 0$

$H_\alpha: \mu_x - \mu_y < 0$

**Step 3**: Specify a test statistic.

$t = \frac{|\bar{x}|}{\sqrt{\frac{s^2}{n}}}$

**Step 4**: Compute the observed value of the test statistic.
```{r}
# Compute the mean difference between the two sample populations
library(UsingR)
data(babies)
diff <- babies$age - babies$dage
n <- length(babies$age - babies$dage) # n = 1236
x_bar <- mean(diff) # mean = -3.365696
sd <- sd(diff) # sd = 6.803471
```

$t = \frac{|-3.365696|}{\sqrt{\frac{6.803471^2}{1236}}}=17.3922$

**Step 5**: Compute the p-value under $H_0$, where $p=P$.
```{r}
t <- 17.3922
n <- length(babies$age - babies$dage)
2 * pt(abs(t), df = n - 1, lower.tail = FALSE) # p-value for paired t-test
```

**Step 6**: Specify a significance level $\alpha$.

We select the p-value range of $(0.01, 0.05]$, making it statistically 
significant and placing it within significance level $\alpha = 0.05$.

**Step 7**: Compare the p-value and the significance level $\alpha$.
The p-value $= 9.029009*10^{-61} < \alpha = 0.05$, indicating that we can reject 
$H_0$; therefore, we conclude that there is a statistically significant
difference between the mothers' ages and the fathers' ages.

```{r}
t.test(babies$age, babies$dage, paired = TRUE, alternative = "two.sided")
```