---
title: "Homework 7"
author: "Kevin Jin"
date: "4/13/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1
```{r}
# Calculate sample mean and standard deviation of the sample mean
x <- 180 
n <- 15; total <- 3500
sigma <- 25
# P(X >= x)
pnorm(total, mean = x * n, sd = sqrt(n) * sigma, lower.tail = FALSE)
```

The probability of a sample of 15 people exceeding 3,500 pounds total is close
to zero at $7.1 * 10^{-17}$; it would be extremely unlikely and near impossible.

## Problem 2
```{r}
# Calculate parameters
n <- 30; total <- 600
lambda <- 25 # mean and variance
sd <- sqrt(lambda)
# P(X >= x)
pnorm(total, mean = lambda * n, sd = sqrt(n) * sd, lower.tail = FALSE)
```

The probability of selling more than 600 bottles in the next 30 days is 1 or 
very close to 1; it is essentially certain.

## Problem 3
```{r}
prop.test(x = 2, n = 30)
```

We are 95% confident that the true proportion of left-handed students is 
between 1.16% and 23.5%; therefore, the 95% confidence interval does contain
the actual value of 13.1%.

## Problem 4
```{r}
library(UsingR)
data(babies)
t.test(babies$age, babies$dage, paired = TRUE)
```

The 95% confidence interval does not contain 0; therefore, we conclude that 0 
is not a reasonable value for the true difference in mean mother's age and 
mean father's age.

For the paired t-test to work, we assume that the response variables (in this
case, the age) are continuous, that both sets of observations are independent
of each other, that both sets of observations follow a normal distribution, 
and that they do not contain outliers.