---
title: "Homework 3"
author: "Kevin Jin"
date: "3/4/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=8)
```

# Problem 1
## Part (a)
```{r}
# Load data
library(ggplot2, warn.conflicts = FALSE)
library(dplyr, warn.conflicts = FALSE)
data("mpg")
# Convert cyl variable from int into ordered factor
mpg$cyl <- factor(mpg$cyl,
                  ordered = TRUE,
                  levels = c("4", "5", "6", "8"))
```
## Part (b)
```{r}
# Convert trans variable from chr into factor
mpg$trans <- substr(mpg$trans, start = 1, stop = 4)
mpg$trans <- factor(mpg$trans,
                    levels = c("auto", "manu"))
```
## Part (c)
```{r}
# Convert drv variable from chr into ordered factor
mpg$drv <- factor(mpg$drv,
                  ordered = TRUE,
                  levels = c("f", "r", "4"))
```
## Part (d)
```{r}
# Convert fl variable from chr into factor
mpg$fl[which(mpg$fl == "p" | mpg$fl == "r")] <- "gasoline"
mpg$fl[which(mpg$fl == "d")] <- "diesel"
mpg$fl[which(mpg$fl == "e" | mpg$fl == "c")] <- "other"
mpg$fl <- factor(mpg$fl,
                 levels = c("diesel", "gasoline", "other"))
```
## Part (e)
```{r}
# Convert class variable from chr into ordered factor
mpg$class <- factor(mpg$class,
                    ordered = TRUE,
                    levels = c("2seater", "subcompact", "compact", 
                                "midsize", "suv", "minivan", "pickup"))
```
## Part (f)
```{r}
# Create new country variable with manufacturer base location
mpg <- mutate(mpg, country = NA)
for (row in 1:nrow(mpg)) {
  if (mpg$manufacturer[row] == "audi" | 
        mpg$manufacturer[row] == "volkswagen") {
    mpg$country[row] <- "germany"
  } else if (mpg$manufacturer[row] == "hyundai") {
    mpg$country[row] <- "south korea"
  } else if (mpg$manufacturer[row] == "land rover") {
    mpg$country[row] <- "great britain"
  } else if (mpg$manufacturer[row] == "honda" | 
             mpg$manufacturer[row] == "nissan" | 
             mpg$manufacturer[row] == "subaru" | 
             mpg$manufacturer[row] == "toyota") {
    mpg$country[row] <- "japan"
  } else {
    mpg$country[row] <- "united states"
  }
}
# Check object structure
str(mpg)
```

# Problem 2
## Part (a)
```{r}
# Draw barplot of country variable and arrange in decreasing order
barplot(sort(table(mpg$country), decreasing = TRUE),
        main = "Frequency of Vehicle Manufacturers by Country (1999-2008)",
        xlab = "Country",
        ylab = "Cars",
        names.arg = c("United States", "Japan", "Germany", 
                      "South Korea", "Great Britain"),
        col = 2,
        cex.main = 1.8,
        cex.lab = 1.5,
        cex.names = 1.5,
        cex.axis = 1.5)
```

The most common country in this dataset is the United States, and the least
common is Great Britain.

## Part (b)
```{r collapse = TRUE}
# Summarize typical US car
names(which.max(table(mpg$displ))) # Engine displacement (liters)
names(which.max(table(mpg$cyl))) # Number of cylinders
names(which.max(table(mpg$trans))) # Transmission type
names(which.max(table(mpg$drv))) # Drive type
names(which.max(table(mpg$fl))) # Fuel type
names(which.max(table(mpg$class))) # Car class
```

| Metric  | Typical US Car |
| ------ | :----: |
| Displacement (liters) | 2 |
| Cylinders | 4 |
| Transmission | Automatic |
| Drive Type | Front-Wheel Drive |
| Fuel Type | Gasoline |
| Car Class | SUV |

## Part (c)
```{r}
# Boxplots of combined mpg of US and Japanese cars
mpg <- mutate(mpg, value = (cty + hwy) / 2) # Create new mpg variable
us <- which(mpg$country == "united states") # Extract indices of US
jp <- which(mpg$country == "japan") # Extract indices of Japan
boxplot(mpg$value[us], 
        horizontal = TRUE,
        main = "Combined MPG of US Cars",
        xlab = "MPG",
        col = "turquoise",
        cex.main = 1.8,
        cex.lab = 1.5,
        cex.axis = 1.5) 
boxplot(mpg$value[jp], 
        horizontal = TRUE,
        main = "Combined MPG of Japanese Cars",
        xlab = "MPG",
        col = "red",
        cex.main = 1.8,
        cex.lab = 1.5,
        cex.axis = 1.5) 
```

```{r collapse = TRUE}
# Numerical summaries of combined mpg of US and Japanese cars
summary(mpg$value[us])
IQR(mpg$value[us], na.rm = TRUE)
sd(mpg$value[us], na.rm = TRUE)

summary(mpg$value[jp])
IQR(mpg$value[jp], na.rm = TRUE)
sd(mpg$value[jp], na.rm = TRUE)
```
| Metric | MPG of US Cars | MPG of Japanese Cars
| ------ | :----: | :----: |
| Mean | 16.64 | 22.66 |
| Median | 15.50 | 22.50 |
| Standard Deviation (2 d.p.) | 3.30 | 4.60 |
| Inter-Quartile Range (2 d.p.) | 4.50 | 7.63 |

## Part (d)
```{r}
# Histograms of engine displacement of US and Japanese cars
hist(mpg$displ[us],
     main = "Histogram of Engine Displacement of US Cars",
     xlab = "Displacement",
     col = "turquoise",
     xlim = c(1, 7),
     cex.main = 1.8,
     cex.lab = 1.5,
     cex.axis = 1.5
     )
hist(mpg$displ[jp],
     main = "Histogram of Engine Displacement of Japanese Cars",
     xlab = "Displacement",
     col = "red",
     xlim = c(1, 7),
     cex.main = 1.8,
     cex.lab = 1.5,
     cex.axis = 1.5
     )
```

| Histogram  | Shape |
| ------ | :----: |
| US Cars | Bimodal |
| Japanese Cars | Left Skewed |