---
title: "Homework 6"
author: "Kevin Jin"
date: "4/10/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1
```{r}
# Simulate 10 flips of a fair coin
x <- c("T", "H")
sample(x, size = 10, replace = TRUE)

# Binomial distribution of Event A (7 or more heads)
p <- dbinom(7, size = 10, prob = 0.5) +
    dbinom(8, size = 10, prob = 0.5) +
    dbinom(9, size = 10, prob = 0.5) +
    dbinom(10, size = 10, prob = 0.5) 
round(p, 2)

# Binomial distribution of Event B (3 heads or less) 
q <- dbinom(4, size = 10, prob = 0.5) +
    dbinom(5, size = 10, prob = 0.5) +
    dbinom(6, size = 10, prob = 0.5) +
    dbinom(7, size = 10, prob = 0.5) + 
    dbinom(8, size = 10, prob = 0.5) +
    dbinom(9, size = 10, prob = 0.5) +
    dbinom(10, size = 10, prob = 0.5) 
p <- 1 - q
round(p, 2)
```

**Derivation:** 

Let the sample space $\Omega$ be the set of all outcomes of flipping a fair 
coin 10 times. Let Event A be the probability of observing 7 or more heads. 
We apply the binomial theorem:

$$P(A) = \sum_{k=7}^{10}\binom{10}{k}(\frac{1}{2})^{k}(\frac{1}{2})^{10-k}$$
$$=\frac{120+45+10+1}{1024}$$
$$=\frac{11}{64}$$
Let Event B be the probability of observing 3 or less heads. Let B' be the 
complement of B, that is, the probability of observing 4 or more heads. We 
apply the binomial theorem again: 

$$P(B') = \sum_{k=4}^{10}\binom{10}{k}(\frac{1}{2})^{k}(\frac{1}{2})^{10-k}$$
$$=\frac{210+252+210+120+45+10+1}{1024}$$
$$=\frac{53}{64}$$
By the complement rule of probability: 

$$P(B) = 1-P(B')$$
$$= 1 - \frac{53}{64}$$
$$= \frac{11}{64}$$

## Problem 2
```{r}
library(ggplot2)

# Guarantee reproducibility
set.seed(20220404)

# Simulate 100 rolls of two six-sided fair dice
# Combined sum is the random variable X
X <- sample(1:6, size = 100, replace = TRUE) + 
  sample(1:6, size = 100, replace = TRUE)

# Plot distribution of results
n <- length(X)
k <- ceiling(sqrt(n)) # Square root choice

ggplot() + 
  geom_histogram(mapping = aes(x = X),
                 bins = k) + 
  labs(x = "Sum of Die Values",
       title = "Histogram of Sums of Die Values from 100 Rolls of Two Fair Dice")

# Sample mean and sample variance
mean(X)
round(var(X), 2)
```

Let $n$ be the number of students in the sample. The sample mean $\bar{x}$ is 
calculated thus: 

$$\bar{x}=\frac{\sum_{k=1}^{n}}{n}$$
$$=6.72$$

Let $x_i$ be the value of one sample. The sample variance $S^2$ is calculated 
thus:

$$S^2=\frac{\sum_{k=1}^{n}(x_i-\bar{x})^2}{n-1}$$
$$=4.95$$

## Problem 3
```{r}
# Probability of 10 or fewer left-handed students in class
y <- pbinom(10, size = 52, prob = 0.131)
```

```{r}
# Bar chart
x <- 0:20 # random variable - how many students are left-handed
y <- dbinom(x, size = 52, prob = 0.131)
ggplot() +
  geom_bar(mapping = aes(x = x, y = y),
           stat='identity') + 
  labs(title = "Probability Mass Function of Left-Handed Students in STAT 3355",
       x = "Number of Left-Handed Students",
       y = "p.m.f")
```

## Problem 4
```{r}
# Probability of a random cereal box having height of <=10.7 in
pnorm(10.7, mean = 12, sd = 0.5)
```

```{r}
# Quantiles of the normal distribution
# 25th
round(qnorm(0.25, mean = 12, sd = 0.5), 2)
# Median
round(qnorm(0.50, mean = 12, sd = 0.5), 2)
# 75th
round(qnorm(0.75, mean = 12, sd = 0.5), 2)
```
