---
title: "Homework 1"
author: "Kevin Jin"
date: "02/04/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1
Find the numeric answers of the following mathematical expressions (up to 2
decimal places if the answer is not an integer).
```{r}
# (a)
round(6 + 5 - 4 / (3) ^ 2, 2)

# (b)
round(exp(sqrt((14 + 13) / (12 + 11))), 2)

# (c)
round(((11 + factorial(12)) / (factorial(13) + 14)), 2)
```

# Problem 2
The monthly sales figures of Hummer H2 vehicles in the U.S. during 2002 were 
2700, 2600, 3050, 2900, 3000, 2500, 2600, 3000, 2800, 3200, 2800, 3400. 
Please answer the following questions.
```{r}
# (a) Enter this data into a data vector called H2
H2 <- c(2700, 2600, 3050, 2900, 3000, 2500, 2600, 3000, 2800, 3200, 2800, 3400)

# (b) Name the data vector with the month abbreviation
names(H2) <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", 
               "Oct", "Nov", "Dec")
# (c) What is the total number of Hummer H2 sold in 2002?
sum(H2)

# (d) Using diff(), find the month with the greatest increase from the previous month, and the month with the greatest decrease from the previous month
diff(H2)
print("Greatest increase: December")
print("Greatest decrease: June")
```

# Problem 3
Rewrite each code block to comply with the “Homework and Project Code 
Style Guide”.
```{r}
x <- c(1, -2, 3, -4, 5, 100)
y <- x * -1
y[y > 0]
```

```{r}
# create a sequence from 1 to 50
z <- seq(1, 50)

# test whether an observation is even
even <- z %% 2 == 0

# subset z by the test above
z <- z[even]
```

```{r}
mean <- function(x) {
  sum(x) / length(x)
}
```

# Problem 4
A twin prime is a prime that has a prime gap of two. Sometimes the term 
twin prime is used for a pair of twin primes. For example, the five twin prime 
pairs are (3, 5), (5, 7), (11, 13), (17, 19) and (29, 31). Write a function 
that returns the number of all twin prime pairs between 1 and a given number n.
```{r}
twin_primes <- function(n) {
  # vector to hold all numbers between 2 and n
  num <- 2:n 
  # logical vector for num to identify primes
  is_prime <- rep(TRUE, length(num)) 
  if (n <= 2) {
    stop("No twin primes between 1-2. Please enter a number greater than 2.")
  } else {
    for (i in 2:length(num)) {
      for (j in 2:(i - 1)) { 
        # skip 3, a special case that breaks the loop
        if (num[i] == 3) { 
          next
        } else if (num[i] %% j == 0) {
          is_prime[i] <- FALSE 
          next
        }
      }
    }
  }
  # create vector with all primes between 2 and n
  primes <- rep(num[is_prime])  
  # counter to track number of twin primes
  count <- 0
  # iterate through primes vector, stopping 1 before the end due to indexing
  for (k in 1:(length(primes)-1)) {
    # if the current entry is 2 less than the next entry, they are twin primes
    if (primes[k + 1] - primes[k] == 2) {
      count = count + 1
    }
  }
  return(count)
}
```
